Heuristics for the Score-Constrained Bin-Packing Problem

### 2018-03-05 PAPER/draft.tex
renamed folders

\title{DRAFT}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\date{\today}

@@

\begin{abstract}
	This version finished: 13/01/2018
\end{abstract}

\section{Introduction}
\label{sec:intro}
The one-dimensional bin packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life sitations.
The BPP can be described as follows: given a set of $n$ items of varying sizes $w$, and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items. As shown by \cite{garey1979}, this problem is NP-hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP. Instead, heursitics can be used to find a near-optimal solution in a shorter amount of time. One example is the greedy heuristic known as first-fit, an online algorithm that places each item (in some arbitrary order) into the lowest-indexed bin. If there are no bins that can feasibly accommodate the item, the algorithm places the item into a new bin. A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins. As proven by \cite{dosa2007} \textcolor{RoyalBlue}{(proved bound is tight)}, the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ \textcolor{RoyalBlue}{(..if the solution has this many bins then it is optimal,} (\citealp{korf2002})).

In 2004, \citeauthor{goulimis2004} brought to light an open-combinatorial problem related to the bin-packing problem. Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consistsing of knives mounted on a bar creates ``scores'' along specific lines on the flat boxes. These scores allow the boxes to be folded in predetermined places. The first stage of this process involves finding a feasible pattern of the flat boxes that minimises the amount of waste, and has been researched extensively. \textcolor{Plum}{It is classically solved by delayed column-generation} (\citealp{gilmore1961, gilmore1963}). However, the second step of this process requires an additional constraint.

The scoring knives, by design, cannot be placed too close together (around 70mm in industry), and as such have a ``minimum knife distance''. The problem then becomes a bin-packing problem with an additional constraint: find a feasible arrangement of boxes such that the sum of two adjacent score widths from different boxes is greater than or equal to the minimum knife distance. \textcolor{RoyalBlue}{We will call this constraint the minimum total score width constraint.}

\textcolor{OrangeRed}{Insert figure, two boxes annotated with score widths, score lines, box widths, knives mounted on bar showing minimum total score width constraint}

\textcolor{RoyalBlue}{Figure showing two boxes with score widths and the scoring knives mounted on a bar. Since the sum of the two adjacent score widths from different boxes is greater than or equal to 70mm, the minimum total width constraint has been met - this is a feasible alignment of these two boxes}

There exists a polynomial time algorithm that is able to recognise whether a particular instance of the problem is feasible or infeasible (\citealp{becker2010}) \textcolor{RoyalBlue}{(i.e. whether all boxes can be arranged in one line)}. However, the algorithm does not consider the lengths of each individual box, or the total length of the final arrangement of boxes. In industry, strips of materials are provided in fixed lengths, so, given a large number of boxes to pack, it may not be feasible to pack all of the boxes onto one strip.

This leads us to our main problem, the score-constrained bin-packing problem: given a collection of boxes with varying widths and score widths on either side, and strips of a fixed length, find the minimum number of strips required to accommodate all of the boxes, such that the minimum total width constraint is met between all boxes on all strips.

The remainder of this report will firstly, in Section \ref{sec:ffdapprox}, introduce the first-fit decreasing approximate algorithm and describe the modifications made to consider the minimum score width constraint. In Section \ref{sec:ffdexact}, we will present a new algorithm which consists of the modified first-fit decreasing algorithm detailed in the previous section combined with a polynomial-time algorithm which will be used to find feasible sub-solutions. A comparison of the two algorithms and an analysis of the results will be provided in Section \ref{sec:compresult}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for furture work.

\section{Formulating the problem}
We are given $n$ boxes that need to be packed onto strips. Each of these boxes have a positive width, and two score widths, one on either side of the box. Since these score widths are not necessarily equal, the boxes can be aligned in two ways: either in a ``regular'' alignment, where the smaller of the two score widths is on the left hand side of the box, or in a ``rotated'' alignment, where the box has been rotated by $180^{\circ}$ so that the larger score width is on the left-hand side of the box. Strips are packed left to right. We also have a finite number of strips of equal fixed lengths. Once a box has been placed onto a strip, the rightmost score on the strip is referred to as the ``free'' score. A box can only be placed onto a strip if it can fit onto the strip, i.e. the addition of the box to the strip doesn't exceed the length of the strip, and if the free score and one of the scores on the box meet the minimum total score width constraint, i.e. the sum of the free score width and one of the scores on the box is greater than or equal to the minimum total score width. Assume that no box has a width that is greater than the fixed length of the strips. \textcolor{RoyalBlue}{need to explain minimum total score width constraint with equation and example, used in the definition for SCBPP below.}

\begin{definition} 
	\label{defn:scbpp}
	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, and a finite number of strips $S_j$ with equal fixed lengths $l$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack all of the boxes such that the minimum total score width constraint is met between every pair of boxes. \textcolor{RoyalBlue}{or: such that for every pair of boxes the sum of the adjacent score widths is greater than or equal to some fixed value $t$.}
\end{definition}

\section{FFD Using Approximate Algorithm}
\label{sec:ffdapprox}

\begin{algorithm}[H]
	\caption{\textcolor{OliveGreen}{Approximate First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
	\label{alg:ffdapprox}
	\begin{algorithmic}[1]
	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, minimum total score width $t$, and a set $\mathcal{S} = \emptyset$.
	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
	\State Sort the boxes in order of non-increasing widths.
	\For{$i \gets 1 \To n$}
		\For{$j \gets 1 \To n$}
			\If{$S_j = \emptyset$}
				\State $S_j \gets \{i_1, i_2\}$
				\State $r(j) \gets r(j) - w(i)$
				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
				\Break
			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
				\If{$w(f_j) + w(i_1) \geq t$}
					\State $S_j \gets S_j \cup \{i_1, i_2\}$
					\State $r(j) \gets r(j) - w(i)$
					\Break
				\ElsIf{$w(f_j) + w(i_2) \geq t$}
					\State $S_j \gets S_j \cup \{i_2, i_1\}$
					\State $r(j) \gets r(j) - w(i)$
					\Break
				\EndIf
			\EndIf
		\EndFor
	\EndFor
	\Return $\mathcal{S}$
	\end{algorithmic}	
\end{algorithm}

\textbf{\textcolor{Rhodamine}{DESCRIPTION OF FFDAPPROX}}

@@

\section{FFD Using Exact Algorithm}
\label{sec:ffdexact}
Introduction

Explanation: Initialise

Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box. We also introduce a ``dummy'' box that has two ``dominating scores'' with widths equal to the minimum total score width, $t$. This dummy box will be discarded at the end of the algorithm, and will not be included in the final feasible alignment. We now have $n$ boxes including the dummy box, and so $G$ will have $2n$ vertices.

We will refer two two vertices that represent either side of the same box as ``partners''. The boxes cannot be altered in any way, and so partners must be adjacent to one another. We therefore create a set of edges, $P$, consisting of edges between partners on $G$. \textcolor{RoyalBlue}{weighted edges $P$}.

Each vertex $v_i$ for $i = 1, 2, ..., 2n$ has a positive value $w(v)$ corresponding to the score width it represents. There is an edge between two vertices $u$ and $v$ on $G$ if and only if the vertices fulfil the \textit{minimum total score width constraint},

\begin{equation*}
	\label{eqn:mtswcg}
	w(u) + w(v) \geq t,
\end{equation*}

and $u$ and $v$ are not partners, i.e. $\{u, v\} \notin P$. The vertices $u$ and $v$ are referred to as \textcolor{OliveGreen}{``matched''}, and so their corresponding score widths can be feasibly aligned next to one another. We now have another set of edges, $Q$, consisting of edges between \textcolor{OliveGreen}{``matched''} vertices.

In order to find a feasible alignment of the boxes, we must find an alternating Hamiltonian cycle on $G$. \textcolor{RoyalBlue}{turns into path when we remove dummy box.}

\begin{definition}
	\label{defn:althamcycle}
	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$. $G$ has an \textit{alternating Hamiltonian cycle} if there exists a Hamiltonian cycle on $G$ such that the successive edges alternate between sets $P$ and $Q$. For example, if vertex $v_k$ in the Hamiltonian cycle is adjacent to vertex $v_{k-1}$ via an edge from $P$, then $v_k$ must be adjacent to vertex $v_{k+1}$ via an edge from $Q$, or vice versa. 
\end{definition}

\textcolor{OrangeRed}{Figure of graph $G$ with boxes, figure of aligned boxes with alternating Hamiltonian path underneath.}

\textcolor{RoyalBlue}{we now need to find a way of producing the alternating hamiltonian cycle on the graph $G$, if one exists.}

MTGMA/MIS

We need to obtain a set of matching edges $M \subset Q$ of cardinality $n$, such that the matching edges from $M$ and the edges from $P$ form an alternating Hamiltonain cycle as described in Definition \ref{defn:althamcycle}. We use a modified matching algorithm (\citealp{mahadev1994, becker2010}) that produces a suitable set of matching edges $M$.

Initially, the vertices are sorted in order of non-decreasing values, and ties are broken arbitrarily. Starting from the smallest vertex, find the largest adjacent vertex (under $Q$? in the set $Q$? )that is not the current vertex's partner, and that has not yet been matched. Add this pair of vertices to the set $M$ that keeps a record of the matching edges, and proceed to the next vertex in the list. Continue until all vertices have been assessed.

If a vertex $v_i$ is not adjacent to any other vertex except its partner, we can rematch previous vertices to provide $v_i$ with a feasible match, provided $v_i$ is not the first vertex in the sorted list, the previous vertex $v_{i-1}$ has a match (i.e. $v_{i-1} \in M$), and $v_{i-1}$ is adajcent to $v_i$'s partner. We then simply match $v_{i-1}$ with $v_i$'s partner, and match $v_i$ with $v_{i-1}$'s previous match. \textcolor{RoyalBlue}{max cardinality.}

If $|M| < n$, then there are not enough matching edges to form an alternating Hamiltonian cycle with the edges in $P$, and therefore there is no feasible arrangement of the boxes such that the minimum total score width constraint is not violated. However, if $|M| = n$, then the graph $G(V, P \cup M)$ is a 2-regular graph, where each vertex is adjacent to one vertex via an edge in $P$, (i.e. its partner), and another vertex via an edge in $M$ (i.e. its match). If $G$ consists of one alternating Hamiltonian cycle, then we simply remove the dominating vertices to obtain a feasible alignment of the boxes/feasible solution. If there are more than two cycles on $G$, we need to combine them into one alternating Hamiltonian cycle. \textcolor{RoyalBlue}{notation number of cycles.}

\textcolor{OrangeRed}{figure of graph $G$ showing edges between partners ($P$), edges in the set $M$, and faint lines to represent the rest of the edges $Q$.}

FCA/Patch

In order to combine multiple cycles into one, we need to replace some matching edges with feasible edges from the set $Q$ that connect vertices from different cycles. \textcolor{RoyalBlue}{The following algorithm is used to find these feasible edges}.

The algorithm initially creates a list of all matching edges in $M$, sorted in order of non-decreasing vertex values \textcolor{RoyalBlue}{(i.e. the edge which connects the smallest vertex to its match is first in the list) (do not include edges from partner swap)}. Starting from the first edge in the list, the algorithm searches through the list of edges until it finds an edge whose smaller vertex is adjacent via an edge in $Q$ to the larger vertex of the succeeding edge in the list, such that both edges are from different cycles on the graph $G$. If such a pair of edges has been found, the algorithm adds the first edge of the pair to a set $C_k$. The algorithm then continues to add all succeeding edges to $C_k$, provided that the smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge via an edge in $Q$, the succeeding edge does not belong to a cycle that is already represented by an edge in $C_k$, and the algorithm has not reached the final edge in the list. Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checks whether this edge is suitable for beginning a new set $C_{k+1}$. If the algorithm has already reached the penultimate or final edge in the list, the algorithm terminates.

@@

\textcolor{RoyalBlue}{Multiple $C_k$ cycles required.}

\begin{algorithm}[H]
	\caption{\textcolor{OliveGreen}{Exact First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
	\label{alg:ffdexact}
	\begin{algorithmic}[1]
	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, and a set $\mathcal{S} = \emptyset$.
	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
	\State Sort the boxes in order of non-increasing widths
	\For{$i \gets 1 \To n$}
		\For{$j \gets 1 \To n$}
			\If{$S_j = \emptyset$}
				\State $S_j \gets \{i_1, i_2\}$
				\State $r(j) \gets r(j) - w(i)$
				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
				\Break
			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
				\State \textcolor{RoyalBlue}{Run} \textcolor{OrangeRed}{``MBAHRA''} \textcolor{RoyalBlue}{on boxes in $S_j$ and box $i$}
				%\Return \textcolor{OrangeRed}{found}
				\If{feasible alignment found}
				%\If{found}
					\State $S_j \gets$ \textcolor{RoyalBlue}{new alignment found by} \textcolor{OrangeRed}{``MBAHRA''}
					\State $r(j) \gets r(j) - w(i)$
					\Break
				\EndIf
			\EndIf
		\EndFor
	\EndFor
	\Return $\mathcal{S}$
	\end{algorithmic}	
\end{algorithm}

\textbf{\textcolor{ProcessBlue}{DESCRIPTION OF FFDEXACT}}

@@

\section{Comparison and Results}
\label{sec:compresult}

\section{Conclusion}
\label{sec:conclusion}

\section{References}
\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}

@@

Lit Review
\begin{itemize}
	\item Solving the one-dimensional bpp using exact methods and heuristics.
	\item Exact methods - \cite{martello1990a} branch and bound based exact algorithm MTP, Carvalho 1999 column generation and branch-and-bound, \cite{eilon1971} depth-first search enumerative algorithm, only solve small size problem instances.
	\item \cite{garey1979} \textcolor{RoyalBlue}{NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.}
	\item \textcolor{RoyalBlue}{Instead, heuristics can be used to find a near optimal solution in a shorter amount of time}.
	\item discuss heuristics.
	\item Explain FF and FFD, online/offline \cite{eilon1971}, \cite{dosa2007} tight bound, optimal number of bins $k$ \cite{korf2002}, complexity $O(n \log n)$ \cite{coffman1984} (where n is the number of items to be packed).
	\item quickly produce a feasible solution, but may not be optimal.
	\item Use heuristics in this paper to find feasible solutions for the problem, why?
\end{itemize}

>>>>

\title{Heuristics for the Score-Constrained Bin-Packing Problem}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\date{\today}

@@

\begin{abstract}

\end{abstract}

\section{Introduction}
%\label{sec:intro}

The one-dimensional bin-packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life situations. The BPP can be described as follows: given a set of $n$ items of varying sizes $w$, and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items. In 2004, \citeauthor{goulimis2004} brought to light an open-combinatorial problem related to the bin-packing problem. Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consisting of knives mounted of a bar creates scores along specific lines on the flat boxes. These scores allow the boxes to be folded in predetermined locations. The first stage of this process is a cutting stock problem, and involves finding a feasible pattern of the flat boxes that minimises the amount of waste. This problem has been researched extensively, and can be solved using delayed column-generation (\citealp{gilmore1961, gilmore1963}). However, the second strip of this process requires an additional constraint.

The scoring knives are arranged in pairs, and cut along score lines from two adjacent boxes simultaneously. By design, the knives cannot be placed too close to one another, and so the distance between the scoring knives must exceed a fixed minimum value $\tau \in \mathbb{R}^{+}$ (around 70mm in industry). The problem therefore consists of finding a feasible arrangement of boxes such that the distance between two score lines is greater than or equal to $\tau$.

There exists a polynomial-time algorithm that is able to recognise whether a particular instance of this problem is feasible (\citealp{becker2010}). However, this algorithm does not consider the widths of each individual box, and only attempts to place the boxes onto a single strip. In industry, strips of material are provided in fixed lengths, and so given a large problem instance multiple strips may be required to feasibly accommodate all of the boxes without exceeding the capacity of the strips.

This leads us to our main problem: given a collection of boxes of varying widths and a finite number of strips of fixed lengths, find the minimum number of strips required to feasibly pack all of the boxes such that the distance between two adjacent score lines on every pair of boxes is greater than or equal to some fixed value $\tau$ on all strips.

The remainder of this article will firstly, in Section \ref{sec:scbpp}, state the notation that will be used throughout, and formally define the problem. Section \ref{sec:ffdapprox} will introduce a modified first-fit decreasing heuristic and describe the changes made to consider the new constraint. In Section \ref{sec:ffdexact}, we will present a new algorithm which consists of the modified heuristic detailed in the previous section combine with a polynomial-time algorithm which will be used to find feasible sub-solutions. A comparison of the two heuristics and an analysis of the results will be provided in Section \ref{sec:comparison}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for future work.

\section{Formulating the Score-Constrained Bin-Packing Problem}
%\label{sec:scbpp}

Despite the simplicity of the bin-packing problem statement, it has in fact been shown to be an NP-hard optimisation problem (\citealp{garey1979}). Thus, under the assumption that $P \neq NP$, there is no known algorithm that is able to find an optimal solution for every instance of the BPP in polynomial time. Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time. One example is the greedy heuristic known as first-fit (FF), an online algorithm that places each item (in some arbitrary order) into the lowest-indexed bin such that the bin capacity is not exceeded. It has been shown that by arranging the items in decreasing order of size, a bin-packing heuristic will produce a solution that is closer to the optimal than if the items are arranged in any other order (\citealp{johnson1974fast}). Applying FF onto items sorted in this manner yields the well-known first-fit decreasing (FFD) heuristic.

An optimal solution of an instance of the BPP is a solution that consists of the fewest number of bins, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by

\begin{equation*}
	k \geq \ceil*{\frac{\sum_{i=1}^{n}w(i)}{c}}
\end{equation*}

where $n$ is the number of items to be packed, $w(i)$ the size of each item $i$, and $c$ the maximum capacity of the bins (\citealp{martello1990b}). In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ bins. More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight. Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time compelexity of FFD is $O(n\log n)$.

---------------------------------

Let each box $i$ of a set of $n$ boxes have a positive width $w(i)$. A ``score width'' is the distance between a score line and the nearest edge of the box. Each box $i$ has two score lines, $i_1, i_2$, with score widths $w(i_1), w(i_2)$ such that $w(i_1) \leq w(i_2)$. Since these score widths are not necessarily equal, each box can be aligned in two distinct ways: in a ``regular'' position, where the smaller score width $w(i_1)$ is on the left-hand side of the box, or in a ``rotated'' position, with the smaller score width on the right-hand side of the box. The boxes can be expressed using their score lines, where $\{i_1, i_2\}$ represents a regular position, and $\{i_2, i_1\}$ a rotated position.

Given the minimum fixed value $\tau$, two boxes can only be placed next to one another if the adjacent score lines $\alpha$ and $\beta$ fulfil the \textit{minimum total score width constraint},

\begin{equation*}
	%\label{eqn:mtswc}
	w(\alpha) + w(\beta) \geq \tau,
\end{equation*}

that is, the sum of the adjacent score widths must exceed the \textit{minimum total score width} $\tau$.

There are a finite number of strips $S_j, j = 1, 2, ...$, with equal fixed lengths $l > 0$, that are to be packed from left to right. Assume that, for all boxes $i = 1, 2, ..., n$, $w(i) \leq l$, and $0 < w(i_1) \leq w(i_2) \leq \tau$. We are now able to present a formal definition of the problem.

\begin{definition}
%	\label{defn:scbpp}
	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, $i = 1, 2, ..., n$, a finite number of strips $S_j$ with equal fixed lengths $l$, and a minimum total score width $\tau$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack the boxes such that the minimum total score width constraint is met between every pair of adjacent boxes. 
\end{definition}

\section{FFD Approx}
%\label{sec:ffdapprox}

The first heuristic to be dicussed is a first-fit decreasing heuristic, modified to account for the minimum total score width constraint. The strips are initially empty, thus we define a residual length $r(j)$ for each strip $S_j, j = 1, 2, ...$. The residual lengths are set equal to the strip lengths $l$, and reduce as boxes are added to the strips. Each strip $S_j$ that is packed with at least one box has a ``free'' score $f_j$, the score on the right-hand side of the last box on the strip. A box can only be placed onto $S_j$ if the box can feasibly fit onto the strip, i.e. the width of th box is less than or equal to the residual length of the strip, and if $f_j$ and the left-hand socre of the box meet the minimum total score width constraint. Since each box has two position, regular and rotated, the heuristic checks if the constraint is met in both positions, favouring the regular position. If a box is only able to fit onto a strip that is empty, then the box is placed onto the strip in a regular position.

\begin{algorithm}[H]
	\caption{\textcolor{OliveGreen}{Approximate First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
%	\label{alg:ffdapprox}
	\begin{algorithmic}[1]
	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, minimum total score width $\tau$, and a set $\mathcal{S} = \emptyset$.
	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
	\State Sort the boxes in order of non-increasing widths.
	\For{$i \gets 1 \To n$}
		\For{$j \gets 1 \To n$}
			\If{$S_j = \emptyset$}
				\State $S_j \gets \{i_1, i_2\}$
				\State $r(j) \gets r(j) - w(i)$
				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
				\Break
			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
				\If{$w(f_j) + w(i_1) \geq \tau$}
					\State $S_j \gets S_j \cup \{i_1, i_2\}$
					\State $r(j) \gets r(j) - w(i)$
					\Break
				\ElsIf{$w(f_j) + w(i_2) \geq \tau$}
					\State $S_j \gets S_j \cup \{i_2, i_1\}$
					\State $r(j) \gets r(j) - w(i)$
					\Break
				\EndIf
			\EndIf
		\EndFor
	\EndFor
	\Return $\mathcal{S}$
	\end{algorithmic}	
\end{algorithm}

@@

\section{FFD Exact}
%\label{sec:ffdexact}

Insert introduction to FFD Exact.

Let each box be represented by two vertices on a graph $G$, one vertex for each side of a box. A ``dummy'' box is introduced, with two ``dominating'' score widths equal to the minimum total score width $\tau$. This dummy box will be discarded at the end of the algorihtm, and will not be included in the final solution. Thus, there are $n$ boxes, including the dummy box, and so $G$ will consist of $2n$ vertices.

Two vertices $v_i, v_j$ $(i \neq j)$ that represent either side of the same box are referred to as ``partners''. The boxes cannot be altered in any way, and so partners must always be adjacent to one another. Therefore, a set $P$ is created, consisting of edges between partners on $G$. These edges are weighted, with values corresponding to the width of the box that the partners are associated with.

Each vertex $v_i, i = 1, 2, ..., 2n$ has a postive value $w(v_i)$ corresponding to the score width it represents. There is an edge between two vertices $v_i, v_j$ $(i \neq j)$ on $G$ if and only if the vertices fulfil the minimum total score width constraint,

\begin{equation*}
	%\label{eqn:mtswcg}
	w(v_i) + w(v_j) \geq \tau,
\end{equation*}

and $v_i, v_j$ are not partners, i.e. $\{v_i, v_j\} \notin P$. The vertices $v_i, v_j$ are then referred to as ``matched'', and so their corresponding score widths can be feasibly placed next to one another. Hence there is another set of edges $Q$, which contains edges between matched vertices.

Thus, $G(V, P\cup Q)$ is an undirected graph with vertex set $V = \{v_1, v_2, ..., v_{2n}\}$, and two edge sets $P$ and $Q$, with $P \cap Q = \emptyset$. In order to find a feasible alignment of the boxes, $G$ must contain an alternating Hamiltonian cycle.

\begin{definition}
	%\label{defn:althamcycle}
	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$. $G$ has an \textit{alternating Hamiltonian cycle} if there exists a Hamiltonian cycle on $G$ such that the successive edges alternate between sets $P$ and $Q$. For example, if vertex $v_i$ in the Hamiltonian cycle is adjacent to vertex $v_{i-1}$ via an edge from $P$, then $v_i$ must be adjacent to vertex $v_{i+1}$ via an edge from $Q$, or vice versa. 
\end{definition}

If $G$ does contain an alternating Hamiltonian cycle, the algorithm simply removes the dominating vertices and any associated edges to obtain an alternating Hamiltonian path, which portrays the order of the score widths that gives rise to a feasible alignment of the boxes. Thus, the aim of the algorithm is to find an alternating Hamiltonian cycle on $G$, if one exists.

The next step of the algorithm attemps to obtain a set of matching edges $M \subset Q$ of cardinality $n$, such that the edges from $M$ and $P$ form an alternating Hamiltonain cycle as described in Definition \ref{defn:althamcycle}. There is a modified matching algorithm (\citealp{mahadev1994, becker2010}) that is able to choose a suitable set of edges for $M$.

Initially, the vertices are sorted in order of non-decreasing values $w(v_i), i = 1,2, .., 2n$, with ties broken arbitrarily. For each vertex in the list, find the largest adjacent vertex in $Q$ that has not yet been added to the matching set $M$. This pair of vertices is then added to $M$, and the algorithm proceeds on to the next vertex in the sorted list. This process continues until all of the vertices have been assessed.

If a vertex $v_i$ is not adjacent to any other vertex except its partner, the previous vertex can be rematched, provided $v_i$ is not the first vertex in the sorted list, the previous vertex $v_{i-1}$ is matched under $M$ (i.e. $v_{i-1} \in M$), and $v_{i-1}$ is adajcent to $v_i$'s partner. Then, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match under $M$. It is guaranteed that this algorithm will produce a maximum cardinality matching $M \subset Q$ (\citealp{becker2010}).

If $|M| < n$, there are not enough matching edges to form an alternating Hamiltonian cycle with the edges in $P$, and therefore there is no feasible arrangement of the boxes such that the minimum total score width constraint is not violated. However, if $|M| = n$, then the graph $G(V, P \cup M)$ is a 2-regular graph where each vertex is adjacent to one vertex (its partner) via an edge in $P$, and another vertex (its match) via an edge in $M$. If $G$ consists of one alternating Hamiltonian cycle, the dominating vertices are removed to obtain a feasible alignment of the boxes. If there are two or more cycles on $G(V, P \cup M)$, a solution to the problem has not yet been found. These cycles need to be combined into one single alternating Hamiltonian cycle.

To merge the multiple cycles on $G$, we need to connect vertices from different cycles by removing some matching edges and adding new edges from $Q$. The following algorithm finds the matching edges on the graph $G(V, P \cup M)$ that allow the cycles to be combined.

The algorithm initially creates a list of all matching edges in $M$, sorted in order of non-decreasing vertex values. Starting from the first edge, the algorithm searches through the list of edges until it finds an edge whose smaller vertex is adjacent via an edge in $Q$ to the larger vertex of the succeeding edge in the list, such that both edges are from different cycles on the graph $G$. If such a pair of edges is found, the first edge of the pair is added to a set $C_k$. The algorithm then continues to add all succeeding edges to $C_k$, provided that the smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge via an edge in $Q$, the succeeding edge does not belong to a cycle that is already represented by an edge in $C_k$, and the algorithm has not reached the final edge in the list. Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checks whether this edge is suitable for beginning a new set $C_{k+1}$. If the penultimate or final edge in the list is reached, the algorithm terminates.

@@

-Multiple $C_k$ cycles required.

\begin{algorithm}[H]
	\caption{\textcolor{OliveGreen}{Exact First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
%	\label{alg:ffdexact}
	\begin{algorithmic}[1]
	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, and a set $\mathcal{S} = \emptyset$.
	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.	
	\State Sort the boxes in order of non-increasing widths
	\For{$i \gets 1 \To n$}
		\For{$j \gets 1 \To n$}
			\If{$S_j = \emptyset$}
				\State $S_j \gets \{i_1, i_2\}$
				\State $r(j) \gets r(j) - w(i)$
				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
				\Break
			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
				\State \textcolor{RoyalBlue}{Run} \textcolor{OrangeRed}{``MBAHRA''} \textcolor{RoyalBlue}{on boxes in $S_j$ and box $i$}
				\If{feasible alignment found}
					\State $S_j \gets$ \textcolor{RoyalBlue}{new alignment found by} \textcolor{OrangeRed}{``MBAHRA''}
					\State $r(j) \gets r(j) - w(i)$
					\Break
				\EndIf
			\EndIf
		\EndFor
	\EndFor
	\Return $\mathcal{S}$
	\end{algorithmic}	
\end{algorithm}

@@

\section{Comparison and results}
%\label{sec:comparison}

\section{Conclusion}
%\label{sec:conclusion}

@@

Lit Review
\begin{itemize}
	\item Solving the one-dimensional bpp using exact methods and heuristics.
	\item Exact methods - \cite{martello1990a} branch and bound based exact algorithm MTP, Carvalho 1999 column generation and branch-and-bound, \cite{eilon1971} depth-first search enumerative algorithm, only solve small size problem instances.
	\item \cite{garey1979} NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.
	\item Instead, heuristics can be used to find a near optimal solution in a shorter amount of time.
	\item discuss heuristics.
	\item Explain FF and FFD, online/offline \cite{eilon1971}, \cite{dosa2007} tight bound, optimal number of bins $k$ \cite{korf2002}, complexity $O(n \log n)$ \cite{coffman1984} (where n is the number of items to be packed).
	\item quickly produce a feasible solution, but may not be optimal.
	\item Use heuristics in this paper to find feasible solutions for the problem, why?
\end{itemize}
